\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-19 paper/main.tex
make snippets 90% of \textwidth
replaced in-text smuggle function example snippets with images

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
\begin{center}
\includegraphics[width=\textwidth]{figs/snippet1.pdf}
\end{center}
Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
\begin{center}
\includegraphics[width=\textwidth]{figs/snippet2.pdf}
\end{center}
However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
\begin{center}
\includegraphics[width=\textwidth]{figs/snippet3.pdf}
\end{center}
Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
\begin{center}
\includegraphics[width=\textwidth]{figs/snippet4.pdf}
\end{center}
\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed. For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
\begin{center}
\includegraphics[width=\textwidth]{figs/snippet5.pdf}
\end{center}

@@

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{verbatim}
smuggle numpy as np    # pip: numpy>1.16,<=1.20 -vv,
\end{verbatim}
the code that is actually executed by the Python interpreter would be
\begin{verbatim}
smuggle(name="numpy", as_="np", installer="pip", args_str="""numpy>1.16,<=1.20 -vv""", installer_kwargs={`editable': False, `spec': `numpy>1.16,<=1.20', `verbosity': 2}).
\end{verbatim}
Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function. It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.

>>>>

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet1.pdf}
\end{center}
Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet2.pdf}
\end{center}
However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet3.pdf}
\end{center}
Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet4.pdf}
\end{center}
\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed. For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet5.pdf}
\end{center}

@@

The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above). When \texttt{davos} is first imported, it is activated automatically. Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer. IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code. The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function. For example, if a user runs a notebook cell containing
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet6.pdf}
\end{center}
the code that is actually executed by the Python interpreter would be
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/snippet7.pdf}
\end{center}
Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly. Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function. It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed. While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.
